---
title: "Homework 8"
author: "Jae Hoon Cho"
date: "November 4, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Read Chapter 21 from “Advanced R” 2nd ed., H. Wickham.

Yes, I read it.

## 2. Complete Problem 1 and Problem 2 from Activity 8 and submit your code to a GitHub repository.
### 2-1. Re-format the code according to the style guide

Before re-format)
```{r}
prime=function(n){
if(n%%1!=0 | n<0){
return (FALSE)
}else if(n==1){
return (FALSE)
}else if(n==2){
return (TRUE)
}else {
for(i in 2:(sqrt(n))){
if(n %% i==0){
return (FALSE)
}}
return (TRUE)
}}
```

After re-format)
```{r}
FindPrime <- function(n) {
# judging number as a prime or not
  if (n %% 1 != 0 | n < 0) {
    return (FALSE)
} else if (n == 1) {
    return (FALSE)
} else if (n == 2) {
    return (TRUE)
} else {
    for (i in 2:(sqrt(n))) {
      if (n %% i == 0) {
        return (FALSE)
      }}
    return (TRUE)
}}
```
### 2-1. Re-format and debug the function find_runs that finds consecutive ones in a given vector.

```{r}
FindConsec <- function(x,k) {
# finds consecutive ones in a given vector
  n <- length(x)
  runs <- NULL
  for (i in 1:(n-k+1)) {
    if (all(x[i:(i+k-1)] == 1)) 
      runs <- c(runs,i)
    } 
  return (runs)
}

FindConsec(c(1,1,0,0,1,1,1,0,1,1,1,1),3)
```

## 3. Please debug the following function that should return a sorted vector in ascending order. For example, if the input for your function is the vector (3, 1, 2), then your function should return the vector (1, 2, 3). Please submit your code to the GitHub repository.

```{r}
SortVec <- function(x) {
# return a sorted vector in ascending order
  if (length(x) == 1) {
    return(x) 
  } else {
    for(last in length(x):2) {
      for(first in 1:(last - 1)) {
        if(x[first] > x[first + 1]) {
          temp <- x[first]
          x[first] <- x[first + 1]
          x[first + 1] <- temp
}}}
    return(x)
}}


test <- c(5,3,7,0,2,9,11,4,6)
SortVec(test)

```
